---
title: "Introduction to ASord"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ASOrd)
```

# Introduction

This is a package for interim analyses with ordinal outcomes, which serves as a complementary to the package `gsDesign`.


# Interim analysis with ordinal outcomes

Assume that the patients in the treatment and control group follows two distinct distributions where the proportional odds assumption holds:

```{r}
data("hold_data")
head(hold_data)
```

To analyze the results for the currently included patients in a clinical trial, execute:

```{r}
y1 = hold_data[hold_data$group == 1, 1]
y0 = hold_data[hold_data$group == 0, 1]

K = 3

interim_odds(K, k = 1, y1, y0)
interim_rank(K, k = 2, y1, y0, A = 6)
```


When the data are generated from the distributions that violate the proportional odds assumption:

```{r}
data("violate_data")
head(violate_data)
```

To analyze the results for the currently included patients in a clinical trial, execute:

```{r}
y1 = violate_data[violate_data$group == 1, 1]
y0 = violate_data[violate_data$group == 0, 1]

K = 3

interim_rank(K, k = 2, y1, y0, A = 6)
```




